Neural networks for solving regression and classification problems

### 2022-11-17 doc/paper.tex
rewrite abstract

>>>>

To rigidly test different models for regression and classification against eachother, we developed a flexible Feed Forward Neural Network that can be specified for various architectures. We used this network to test different schedulers, activation functions and model complexities in order to achieve a balance of satisfying results and low computational cost accross different datasets. Pitting the schedulers against eachother to fit a polynomial approximation of the Franke Function using linear regression, Adam and Adagrad came out on top, with Adagrad using less time to complete the fit. Furthermore, Adagrad's cross validated test MSE of 0.011 being slightly lower than Adam's 0.012 when ran for 5000 epochs. For neural networks problems, Adam proved to be the superior scheduler, ---
